Towards Compiler-Agnostic Performance in Finite-Difference Codes

### 2015-09-15 docs/papers/shallow_performance/shallow_perf.tex
parco paper: added labels to optimisation plot. Changed numbering of transformations so indexed from 1 instead of 0.

\begin{figure}[!t]
\centering
\includegraphics[width=123mm]{opt_stages_256}
\caption{The performance of the \psykal\ version of Shallow for the
  $256^{2}$ domain at each stage of optimisation. Results are given as
  a percentage of the performance of the original code for each
  compiler/CPU combination.}
\label{FIG_opt_stages_256}
\end{figure}

>>>>

\begin{figure}[!t]
\centering
\includegraphics[width=\textwidth]{opt_stages_256}
\caption{The performance of the \psykal\ version of Shallow for the
  $256^{2}$ domain at each stage of optimisation. Results are given as
  a percentage of the performance of the original code for each
  compiler/CPU combination. As an aid to understanding, significant
  performance jumps are labelled with the corresponding transformation
  number.}
\label{FIG_opt_stages_256}
\end{figure}
